---
title: "FA-7, YANG"
output: html_document
date: "2023-04-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EXERCISES 5.1 

**1**. A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet   the design criterion, and must be scrapped.

**(a)** Calculate the probability that a memory stick will be scrapped.


```{r A}
a <- 2
b <- 12
c <- 10
g <- 1/(b-a)
#the memory sticks scrapped when it longer then 10mm
Pscrapped <- g*(b-c)
Pscrapped
```

**(b)** Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance

```{r B}
memorysticks <- runif(50,min=2, max=12)
memorysticks
hist(memorysticks, main="memorysticks")
```

  Get the mean and variance

```{r Bmean&variance}
mean <- mean(memorysticks)
mean
variance <- var(memorysticks)
variance
```

**2**. Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X  follows the pdf

  ***F(x) = 0.025x + b, 2 < x < 6***
                                                 
**(a)** Show that, for this to be a genuine probability density, b = 0.15.
 
    "∫(0.025x+b)dx" is equal to 1 when integrated over the interval [2, 6]
  
    ∫(0.025x+b)dx=0.0125x^2+bx+C 
   
    (0.0125*6^2+6b)-(0.0125*2^2+2b)=1
   
    1=(0.0125*36+6b)-(0.0125*4+2b)
   
    1=0.45+6b-0.05-2b
   
    1=0.4+4b
   
    so we have b=0.15.
    
    
**(b)** Find the probability that the measurement of the current exceeds 3 A.

    P(X > 3) = ∫(0.025x + 0.15) dx on the interval [3, 6]

```{r 2b}
z <- 0.0125
x <- 0.15
v <- 3
m <- 6
PGreaterthen3 <- (z*(m^2)+x*m)-(z*(v^2)+x*v)
PGreaterthen3

```
The probability that the measurement of the current exceeds 3 A is 0.7875 or 78.75%.


**(c)** Find E(X).

    E(X)=∫(x*(0.025x+0.15)) dx integrates over the interval [2, 6]
    
    ∫(0.025*x^2+0.15x)dx=(1/3)*0.025*x^3+0.075x^2+C
```{r 2c}
p <- 0.025
l <- 0.075
k <- 2
o <- 6
EX <- (1/3*p*o^3+l*o^2)-(1/3*p*k^3+l*k^2) 
EX

```
So, E(X) ≈ 4.1.


**3**. In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in [−π,+π]. Find P(X ≤ 0) and P(X ≤ π∕2)

**f(x) = 1 / (b - a)**

On the interval [−π,+π], the probability density function f(x)=1/(2π).

Find P(X ≤ 0)

We need to compute the integral of f(x) over the interval [−π,0]:

P(X≤0)=∫(1/(2π))dx

(0/(2π))-((-π)/(2π))=π/(2π) =0.5

so P(X≤0)= 0.5


Find P(X ≤ π∕2)

P(X≤π∕2)=∫(1/(2π))x on the interval [−π, π∕2]

(π/(4* (2π)))-((-π)/(2* (2π)))=(3π)/(4*(2π))=3/4

so P(X≤π∕2)=3/4
